Covariate analysis of ROSMAP reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-03-23 code/Rmd/ROSMAP_REPROCESSED.Rmd
Minor sanity fix in ROSMAP reprocessing

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
  group_by(Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05)

tmp1 = DE %>%
  dplyr::filter(adj.P.Val <= 0.05, abs(logFC) >= log2(1.2)) %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
  group_by(Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2)

kable(full_join(tmp %>%
                  dplyr::rename(DOWN_FDR_0_05 = DOWN, UP_FDR_0_05 = UP),
                tmp1 %>%
                  dplyr::rename(DOWN_FDR_0_05_FC_1.2 = DOWN, UP_FDR_0_05_FC_1.2 = UP)))

>>>>

writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
tmp = DE %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
  group_by(Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)
